Cover Letter

### 2023-11-02 cover.qmd
Update

We kindly request your consideration of the manuscript entitled "Corticosteroids for improving outcomes in HELLP syndrome: a systematic review and meta-analysis" for publishing in BMJ Open.

>>>>

We kindly request your consideration of the manuscript entitled "Corticosteroids for improving patient relevant outcomes in HELLP syndrome: a systematic review and meta-analysis" for publishing in BMJ Open.
